# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data

```{r}
unzip("activity.zip")
act <- read.csv("activity.csv")
act <- transform(act,date = as.Date(date))
```

## What is mean total number of steps taken per day?

```{r total steps}
sum_steps <- tapply(act$steps, act$date, sum, na.rm = T)
hist(sum_steps, main = "steps of each day",xlab = "total steps")
dev.off()
```

```{r}
mean_steps <- tapply(act$steps, act$date, mean, na.rm = T)
median_steps <- tapply(act$steps, act$date, median, na.rm = T)
report <- cbind(mean_steps, median_steps)
colnames(report) <- c("mean","median")
report
```

## What is the average daily activity pattern?

```{r}
ave_steps <- tapply(act$steps, act$interval, mean, na.rm = T)
plot(unique(act$interval), ave_steps, type = "l", xlab = "interval", ylab = "number of steps",main = "number of steps each day")
dev.off()
wr <- names(which.max(ave_steps))
```

* The "`r wr`" interval contains the maximum number of steps across the days in the dataset.

## Imputing missing values

```{r}
nas <- is.na(act$steps)
num_nas <- sum(nas)
```

* There are `r num_nas` NAs in the dataset.

* Filling in all of the missing values in the dataset with the mean of the 5-minute interval steps.

```{r}
newact <- act
newact[nas,"steps"] <- ave_steps
```

```{r}
newsum_steps <- tapply(newact$steps, newact$date, sum, na.rm = T)
hist(newsum_steps, main = "steps of each day(new)", xlab = "total steps")
dev.off()
```

```{r}
newmean_steps <- tapply(newact$steps, newact$date, mean, na.rm = T)
newmedian_steps <- tapply(newact$steps, newact$date, median, na.rm = T)
new_report <- cbind(newmean_steps, newmedian_steps)
colnames(new_report) <- c("new_mean","new_median")
new_report
```

* There are no differences between these values and the estimates from the first part of the assignment.

* Imputing missing data on the estimates of the total daily number of steps removes the NAs and make the dataset clean with the statistical informations unchanged.

## Are there differences in activity patterns between weekdays and weekends?

```{r}
Sys.setlocale(locale = "C")
wkday <- weekdays(newact$date)
week <- character(length(newact$date))
for(i in seq(week)){
        if(wkday[i] == "Saturday"|wkday[i] == "Sunday")
                week[i] = "weekend"
        else
                week[i] = "weekday"
}
week <- as.factor(week)
```

```{r}
mean1 <- tapply(newact[week == "weekday","steps"],newact[week == "weekday","interval"],mean)
mean2 <- tapply(newact[week == "weekend","steps"],newact[week == "weekend","interval"],mean)

par(mfrow = c(2,1))
plot(unique(newact$interval),mean1, main = "weekday", type = "l", xlab = "interval", ylab = "number of steps")
plot(unique(newact$interval),mean2, main = "weekend", type = "l", xlab = "interval", ylab = "number of steps")
dev.off()
```